### 2013-11-11 article2013.Rmd
Tried out the country grouping. I will leave it out from the presentation and paper, too. Edited the tables, but many issues still remains, mainly explaining the analysis and later intrepretations

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("article2013.Rmd")
system("~/.cabal/bin/pandoc article2013.md --template=../../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --toc --latex-engine=xelatex -V lang=en -V papersize:a4paper -V documentclass=scrreprt -o article2013.pdf")
# Kuvat kohdalleen - avaa päätte
~/.cabal/bin/pandoc article2013.md --template=../../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --toc --latex-engine=xelatex -V lang=en -V papersize:a4paper -V documentclass=scrreprt -o article2013.tex
sed -i 's/begin{figure}\[htbp\]/begin{figure}\[H\]/g' article2013.tex
xelatex article2013.tex

@@

-----------------------------------------------------------------------------
Variable                          Description
------------------------          -------------------------------------------------
**Individual-level**

Transfer dependency               Social or private transfers as main source of income

Low education                     No or only compulsory level education

Perceived low income level        Perceived income level below the country median

Income compared to past           Perceived change in income compared to situation in four years ago

Income compared to future         Expected change in income over the next four years

Effect of financial crises        Whether respondents perceives that their household has suffered the financial crisis great or fair amount

@@

Ghange in total GDP 2007 – 2010   Relative change from 2007 to 2010

Gini coefficient                  Measures the distribution of income or consumption expenditure among individuals or households

Voice and Accountability          Indicators measuring the political process, civil liberties and political rights. These indicators measure the extent to which citizens of a country are able to participate in the selection of governments. Indicators measuring the independence of the media is also included.
Description
-----------------------------------------------------------------------------

@@

TÄMÄ YLLÄ MAINITTU TEKSTI VOIDAAN KUITATA SÄRMÄSTI SILLÄ ETTÄ LISÄTÄÄN TUOHON TABLE 2:EN OIKEALLE PUOLELLE YKSI SARAKE OTSIKOLLA "DATA SOURCE" SIIHEN SITTEN INDIVIDUAL-LEVEL MUUTTUJIEN KOHDALLE JOKA RIVILLE LIFE IN TRANSITION SURVEY JA MAKROMUUTTUJIEN KOHDALLE TYYLIIN WORLD BANK 2013 JA SITTEN LÄHTEISIIN LÄHDEVIITEMERKINNÄT NÄILLE ELI WORLD BANK (2013) JA ONLINEVIITTAUS LEHDEN SÄÄTÖJEN MUKAISESTI.

The empirical section starts by presenting the results of descriptive analyses. As we assume that individual level perceptions are dependent both on individual and country-level contextual factors, it is recommended to use multilevel regression analysis for this task (Snijders \& Bosker, 2011).  Multilevel analysis requires hierarchical dataset and allows the estimation of country-level effects on individual level outcomes. The analysis is performed using lmer-function from lme4 package in R [^*****]. All of the models employed are so called multilevel logistic random intercept models at the level of individuals and countries.

[^*****]:R-code for data transformation and analysis is available at [http://research.muuankarski.org/attributions/](http://research.muuankarski.org/attributions/)

TÄTÄ YLLÄ MAINITTUA ALAVIITETTÄ EI VARMAANKAAN SAA LAITTAA SUBMITTED-VERSIOON. SE VOIDAAN HALUTTAESSA LISÄTÄ SITTEN KUN PAPERI ON HYVÄKSYTTY LEHTEEN.

Our multilevel modelling focuses first in bivariate connections between two dependent variables and both individual and country level independent variables(See Appendix B). At the second step we include all individual level variables to a single model (models sb1 and ib1). Then we add each of the four country level variables one at the time (models sb2/ib2 - sb5/ib5). With limited number of countries we are obliged to use only few contextual variables. Tables will include both a fixed effects and a random effects part. The fixed effects part will include odds ratios and statistical significances of independent variables, while the random effects part will indicate the country-level variance and standard deviation, deviance and number of cases and groups. Full model summaries currently available at [http://research.muuankarski.org/attributions/](http://research.muuankarski.org/attributions/).

@@

@@

texreg(list(soc.0,
        soc.1,
        soc.2,
        soc.3,
        soc.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        use.packages=TRUE,
        #sideways=TRUE,
        scriptsize=TRUE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)

```{rarticleModelsInd, results='asis', eval=TRUE}
texreg(list(ind.0,
        ind.1,
        ind.2,
        ind.3,
        ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        use.packages=TRUE,
        include.pvalues=TRUE,
        #sideways=TRUE,
        scriptsize=TRUE,
        caption="Logistic multilevel random intercept model for individual blame type of explanation", 
        caption.above=TRUE)

>>>>

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("article2013.Rmd")
system("~/.cabal/bin/pandoc article2013.md --template=../../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --toc --latex-engine=xelatex -V lang=en -V papersize:a4paper -V documentclass=scrreprt -o article2013.pdf")
# Kuvat kohdalleen - avaa päätte
~/.cabal/bin/pandoc article2013.md --template=../../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --toc --latex-engine=xelatex -V lang=english -V papersize:a4paper -V documentclass=scrreprt -o article2013.tex
sed -i 's/begin{figure}\[htbp\]/begin{figure}\[H\]/g' article2013.tex
xelatex article2013.tex

@@

--------------------------------------------------------------------------------------------
Variable                          Description                                                                                                   Source
------------------------          ------------------------                                                                                      -----------
**Individual-level**

Transfer dependency               Social or private transfers as main source of income                                                          lits

Low education                     No or only compulsory level education                                                                         lits

Perceived low income level        Perceived income level below the country median                                                               lits

Income compared to past           Perceived change in income compared to situation in four years ago                                            lits

Income compared to future         Expected change in income over the next four years                                                            lits

Effect of financial crises        Whether respondents perceives that their household has suffered the financial crisis great or fair amount     list

@@

Ghange in total GDP 2007 – 2010   Relative change from 2007 to 2010                                                                             World Bank

Gini coefficient                  Measures the distribution of income or consumption expenditure among individuals or households                World Bank

Voice and Accountability          Indicators measuring the political process, civil liberties and political rights.                             World Bank
--------------------------------------------------------------------------------------------

@@

The empirical section starts by presenting the results of descriptive analyses. As we assume that individual level perceptions are dependent both on individual and country-level contextual factors, it is recommended to use multilevel regression analysis for this task (Snijders \& Bosker, 2011).  Multilevel analysis requires hierarchical dataset and allows the estimation of country-level effects on individual level outcomes. The analysis is performed using lmer-function from lme4 package in R. All of the models employed are so called multilevel logistic random intercept models at the level of individuals and countries.

Our multilevel modelling focuses first in bivariate connections between two dependent variables and both individual and country level independent variables(See Appendix B). At the second step we include all individual level variables to a single model (models sb1 and ib1). Then we add each of the four country level variables one at the time (models sb2/ib2 - sb5/ib5). With limited number of countries we are obliged to use only few contextual variables. Tables will include both a fixed effects and a random effects part. The fixed effects part will include odds ratios and statistical significances of independent variables, while the random effects part will indicate the country-level variance and standard deviation, deviance and number of cases and groups.

*A more throughout description of modelling will be added as the final details in modelling will be decided*

@@

*Results and conclusions are not yet reshaped to match the recent changes in the analysis...*

@@

model.names.multi.A = c("SB empty",
                      "SB individual",
                      "SB all",
                      "IB empty",
                      "IB individual",
                        "IB all")

texreg(list(soc.0,soc.1,soc.4,
            ind.0,ind.1,ind.4),
        custom.model.names = model.names.multi.A,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        use.packages=TRUE,
        #sideways=TRUE,
        scriptsize=TRUE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)

### 2013-11-11 finalPlots.Rmd
Tried out the country grouping. I will leave it out from the presentation and paper, too. Edited the tables, but many issues still remains, mainly explaining the analysis and later intrepretations

ppi <- 300
png("figure/scatter_gdp.png", width=12/2.54*ppi, height=18/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()
```

@@

ppi <- 300
png("figure/scatter_gini.png", width=12/2.54*ppi, height=18/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()
```

@@

>>>>

ppi <- 300
png("figure/scatter_gdp.png", width=12/2.54*ppi, height=18/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

png("figure/scatter_gdpSB.png", width=12/2.54*ppi, height=8/2.54*ppi, res=ppi)
plot1
dev.off()
png("figure/scatter_gdpIB.png", width=12/2.54*ppi, height=8/2.54*ppi, res=ppi)
plot2
dev.off()

@@

ppi <- 300
png("figure/scatter_gini.png", width=12/2.54*ppi, height=18/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

png("figure/scatter_giniSB.png", width=12/2.54*ppi, height=8/2.54*ppi, res=ppi)
plot1
dev.off()
png("figure/scatter_giniIB.png", width=12/2.54*ppi, height=8/2.54*ppi, res=ppi)
plot2
dev.off()
```

@@

png("figure/scatter_wbgiSB.png", width=12/2.54*ppi, height=8/2.54*ppi, res=ppi)
plot1
dev.off()
png("figure/scatter_wbgiIB.png", width=12/2.54*ppi, height=8/2.54*ppi, res=ppi)
plot2
dev.off()

### 2013-11-11 index.Rmd
Tried out the country grouping. I will leave it out from the presentation and paper, too. Edited the tables, but many issues still remains, mainly explaining the analysis and later intrepretations

cd ~/workspace/lits/attrib/attrib_year2013/
lftp -u np16003 -e "mput *.html *.Rmd *.pdf *.epub *.docx;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/

@@

@@

date      comment
--------  -------------------
20131103  Regression modelling in process. Final models will be published on Tuesday afternoon
20131105  Regression modelling almost finished. Bug in a software caused a delay. Will be fixed by Wed morning. Now the tables are there, but coef and model names are not customized.
20131106  Regression modelling somewhat done for Turku seminar.
20131109  Corrections from Turku and the text restuctured. Methods needs to be opened

@@

[Final tables](finalTables.html)                          [source](finalTables.Rmd)
-------------------

@@

- HSE Moscow - November 12, 2013
- [Jatkokoulutusseminaari Turku November 7, 2013](turku2013/slidesTkuJatko20131107.html)
- [ESA Torino - August 29, 2013](torino2013/TorinoSlides2013_final.html)

>>>>

cd ~/workspace/lits/attrib/attrib_year2013/
lftp -u np16003 -e "mput *.html *.Rmd *.pdf;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/

@@

cd ~/workspace/lits/attrib/attrib_year2013/moscow2013
lftp -u np16003 -e "mput *.html;quit" ftp://np16003@www.muuankarski.org/domains/muuankarski.org/public_html/research/attributions/moscow2013

@@

date      comment
--------  -------------------
20131103  Regression modelling in process. Final models will be published on Tuesday afternoon
20131105  Regression modelling almost finished. Bug in a software caused a delay. Will be fixed by Wed morning. Now the tables are there, but coef and model names are not customized.
20131106  Regression modelling somewhat done for Turku seminar.
20131109  Corrections from Turku and the text restuctured. Methods needs to be opened
20131111  Presentation for HSE conference and improving the text a bit

@@

-------------------

@@

- [HSE Moscow - November 12, 2013](moscow2013/lcsr20131112.html)
- [Jatkokoulutusseminaari Turku November 7, 2013](turku2013/slidesTkuJatko20131107.html)
- [ESA Torino - August 29, 2013](torino2013/TorinoSlides2013_final.html)

### 2013-11-11 mapPlots.Rmd
Tried out the country grouping. I will leave it out from the presentation and paper, too. Edited the tables, but many issues still remains, mainly explaining the analysis and later intrepretations

ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = socialBlame)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top")
```

@@

```{rmapPlotsDV2}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = individualBlame)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top")
```

@@

```{rmapPlotsDV3}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = socialFate)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top")
```

@@

```{rmapPlotsDV4}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = individualFate)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top")
```

@@

```{rmapPlotsDV5}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = not.stated)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top")
```

@@

```{rmapPlotsDV6}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = dont.know)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top")
```

@@

```{rmapPlotsIvMacro1}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = gdpchange07.10)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low=muted("red"), high=muted("blue")) +
  theme(legend.position="top")
```

@@

```{rmapPlotsIvMacro2}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = uw_gini)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low=muted("blue"), high=muted("red"), midpoint=33.55) +
  theme(legend.position="top")
```

@@

```{rmapPlotsIvMacro3}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = wbgi_vae)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low=muted("red"), high=muted("blue")) +
  theme(legend.position="top")
```

>>>>

ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = socialBlame)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsDV2}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = individualBlame)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsDV3}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = socialFate)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsDV4}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = individualFate)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsDV5}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = not.stated)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsDV6}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = dont.know)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low="white", high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsIvMacro1}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = gdpchange07.10)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low=muted("red"), high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsIvMacro2}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = uw_gini)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low=muted("blue"), high=muted("red"), midpoint=33.55) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```

@@

```{rmapPlotsIvMacro3}
ggplot(plotMap, aes(long,lat,group=group)) +
  geom_polygon(data = map.df, aes(long,lat), fill="gray90", color = "white") +
  geom_polygon(aes(fill = wbgi_vae)) +
  geom_polygon(data = plotMap, aes(long,lat), 
               fill=NA, color = "white", size=0.1) +
  coord_map(project="orthographic") +
  scale_fill_gradient2(low=muted("red"), high=muted("blue")) +
  theme(legend.position="top") +
  theme(legend.text = element_text(size=14))
```
